---
title: "PsyOLAD Meta Analysis Script"
author: "Zack Williams"
date: "2023-07-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(metafor,brms,bayestestR)
df <- read.csv('test_data_v3.csv')
df$dtype <- as.factor(df$dtype)
df$design <- as.factor(df$design)
df$scale <- as.factor(df$scale)
df$bsl <- df$pep <- NULL
df <- df %>% pivot_wider(names_from = c(tp_tag),values_from = c(mean,se,std,var)) 
df <- df[df$study %in% unique(df$study)[1:85],] # Include only first 85 unique studies to have roughly approximate-sized corpus
set.seed(420)
df1 <- df[sample(1:nrow(df),size = 150),] # Now sample 150 rows total to include variable numbers of measures per study
df1$effect <- 1:nrow(df1) # Number the effects 
df2 <- df[which(df$dtype=="psy")[1:45],]
df2$effect <- 1:nrow(df2)
df3 <- df[which(df$dtype=="ssri"),]
df3$effect <- 1:nrow(df3)

# Priors
prior_mods <- c(prior(student_t(3,-10,3),class="Intercept"),
  prior(normal(0, 3),class="b"),
  prior(normal(0,0.5),class="b",coef = "mean_bsl"),
  prior(cauchy(0,1), class = "sd"),
  prior(cauchy(0,0.3), class = "sd",coef="mean_bsl",group="study"),
  prior(cauchy(0,0.3), class = "sd",coef="mean_bsl",group="study:effect"),
  prior(cauchy(0,0.3), class = "sd",coef="mean_bsl",group="scale"),
  prior(lkj(2),class="cor")
  )

# Model formulae
bf_mod1 <- bf(mean_pep | se(se_pep)  ~ mean_bsl + dtype +  (1 + mean_bsl + dtype|study) + (1 + mean_bsl + dtype |study:effect) + (1 + mean_bsl + dtype |scale))

bf_mod23 <- bf(mean_pep | se(se_pep)  ~ mean_bsl + is_blind +  (1 + mean_bsl + is_blind|study) + (1 + mean_bsl + is_blind |study:effect) + (1 + mean_bsl + is_blind |scale))
```


PRIORS:

INTERCEPT: Student t3(-10, 3)
Beta [BSL]: Normal(0, 0.5)
Beta [STUDY_TYPE, BLIND, INTERACTION]: Normal(0, 3)
SD (i.e., tau) [BSL]: Half-Cauchy(0, 0.3) 
SD (i.e., tau) [STUDY_TYPE, BLIND, INTERACTION]: Half-Cauchy(0, 1)
COR: LKJ(2)

Model 1: (PAT > OLAD at primary outcome timepoint) 

BRMS model formula: ENDPOINT_HAMD | se(SE_ENDPOINT_HAMD)  ~ BSL_HAMD + STUDY_TYPE +  (1 + BSL_HAMD + STUDY_TYPE|study) + (1 + BSL_HAMD + STUDY_TYPE |study:effect) + (1 + BSL_HAMD + STUDY_TYPE |measure)

Hypothesis operationalization: one-sided Bayes factor for fixed effect of STUDY_TYPE exceeding HAMD17 MCID ≥ 3. Posterior probability of hypothesis will also be reported (>95% deemed very strong support for non-equivalence hypothesis). 

Model 2 (OL PAT = Blinded PAT at primary outcome timepoint)

BRMS model formula: ENDPOINT_HAMD | se(SE_ENDPOINT_HAMD)  ~ BSL_HAMD + BLINDED +  (1 + BSL_HAMD + BLINDED |study) + (1 + BSL_HAMD + BLINDED |study:effect) + (1 + BSL_HAMD + BLINDED |measure)

Hypothesis operationalization: two-sided Bayes factor for fixed effect of BLINDED exceeding HAMD17 MCID ≤ 1/3. Posterior probability of hypothesis will also be reported (<5% deemed very strong support for equivalence hypothesis; 5-10% and 10-15% deemed strong and moderate support for equivalence hypothesis). 

Model 3 (OL AD > Blinded AD at primary outcome timepoint)

BRMS model formula: ENDPOINT_HAMD | se(SE_ENDPOINT_HAMD)  ~ BSL_HAMD + BLINDED +  (1 + BSL_HAMD + BLINDED |study) + (1 + BSL_HAMD + BLINDED |study:effect) + (1 + BSL_HAMD + BLINDED |measure)

Hypothesis operationalization: two-sided Bayes factor for fixed effect of BLINDED exceeding HAMD17 MCID ≥ 3. Posterior probability of hypothesis will also be reported (>95% deemed very strong support for non-equivalence hypothesis). 

```{r}
mod1_test <- brm(bf_mod1,family = gaussian(),
                 data = df1,prior = prior_mods,
                 chains = 12,cores=15,backend="cmdstanr",
                 warmup = 2000, iter=5000,control = list(adapt_delta=0.999,max_treedepth=20)
                 )

bf_rope(as_draws_df(mod1_test)$b_dtypessri,prior=rnorm(36000,0,3),null = c(-3,3)) # 1.40 for 2-sided BF
bf_rope(as_draws_df(mod1_test)$b_dtypessri,prior=rnorm(36000,0,3),null = c(-Inf,3)) # 3.40 for 1-sided BF
mean(as_draws_df(mod1_test)$b_dtypessri > 3) # 39.3% of posterior > MCID [fairly weak support for non-equivalence]

mod2_test <- brm(bf_mod23,family = gaussian(),
                 data = df2,prior = prior_mods,
                 chains = 12,cores=15,backend="cmdstanr",
                 warmup = 2000, iter=5000,control = list(adapt_delta=0.999,max_treedepth=20)
                 )

bf_rope(as_draws_df(mod2_test)$b_is_blindTRUE,prior=rnorm(36000,0,3),null = c(-3,3)) # 0.162 for 2-sided BF
mean(abs(as_draws_df(mod2_test)$b_is_blindTRUE) < 3)

mod3_test <- brm(bf_mod23,family = gaussian(),
                 data = df3,prior = prior_mods,
                 chains = 12,cores=15,backend="cmdstanr",
                 warmup = 2000, iter=5000,control = list(adapt_delta=0.999,max_treedepth=20)
                 )

bf_rope(as_draws_df(mod3_test)$b_is_blindTRUE,prior=rnorm(36000,0,3),null = c(-3,3)) # 5.86 for 2-sided BF
bf_rope(as_draws_df(mod3_test)$b_is_blindTRUE,prior=rnorm(36000,0,3),null = c(-Inf,3)) # 14.88 for 1-sided BF
mean(as_draws_df(mod3_test)$b_is_blindTRUE > 3) # 73.6% of posterior > MCID [moderate support for non-equivalence]
```


















